% !TEX encoding = UTF-8

%======中文摘要内容格式:{中文摘要}{关键词}
\ZhAbstract{
青海大学（Qinghai University），位于青海省西宁市，是一所以工、农、医、管四大学科为主，其他学科协调发展的教学研究型大学，国家“双一流”建设高校，国家“211工程”重点建设大学，是清华大学等6所知名高校的对口支援学校，是全国14所“中西部高校提升综合实力”工程入选高校，国家首批百所创新示范校，教育部与青海省人民政府部省合建高校，具有学士、硕士、博士学位授予权。

学校前身为青海工学院，始建于1958年。1960年11月，与青海农牧学院、青海医学院、青海财经学院合并为青海大学，“文革”初期被撤销。1971年恢复青海工农学院，设有工、农两大学科。1988年恢复青海大学。1997年10月，青海畜牧兽医学院并入青海大学。2001年1月，青海省农林科学院、青海省畜牧兽医科学院、青海财经职业学院整建制划归青海大学，2004年青海医学院并入，组建成新的青海大学。

截至2022年1月，学校占地3000余亩；有本科专业67个，博士后科研流动站1个，一级学科博士学位授权点5个，一级学科硕士学位授权点20个，交叉学科硕士学位授权点1个，二级学科硕士学位授权点共计108个；有硕士专业学位授权类别15个，共计96个专业领域；有教职工5356人（含附属医院3054人），专任教师1451人，在校生2.5万余人，其中研究生3714人、本专科生1.9万余人（含昆仑学院3838人）。}{青海大学；211大学；双一流建设高校}
%======中文摘要内容格式:{英文摘要}{关键词}
\EnAbstract{
Qinghai University, located in Xining City, Qinghai Province, is a teaching and research university with four major disciplines: engineering, agriculture, medicine and management, and coordinated development of other disciplines. "It is also one of the 14 universities selected for the project of "Midwest Universities to Improve Comprehensive Strength", the first batch of 100 innovative demonstration universities, and the university jointly built by the Ministry of Education and Qinghai Provincial People's Government, with the right to confer bachelor, master and doctoral degrees. It has the right to confer bachelor, master and doctoral degrees.
	
In November 1960, it was merged with Qinghai Agricultural and Animal Husbandry College, Qinghai Medical College and Qinghai Finance and Economics College to form Qinghai University, which was abolished at the beginning of the Cultural Revolution. 1971, Qinghai Agricultural and Industrial College was restored, with two major disciplines of engineering and agriculture, and Qinghai University was restored in 1988. In October 1997, Qinghai College of Animal Husbandry and Veterinary Medicine was incorporated into Qinghai University, and in January 2001, Qinghai Academy of Agriculture and Forestry, Qinghai College of Animal Husbandry and Veterinary Medicine and Qinghai College of Finance and Economics were incorporated into Qinghai University, and in 2004, Qinghai College of Medicine was incorporated into Qinghai University.

As of January 2022, the university covers an area of more than 3,000 mu; there are 67 undergraduate programs, 1 postdoctoral research station, 5 authorized doctoral degree programs in primary disciplines, 20 authorized master's degree programs in primary disciplines, 1 authorized master's degree program in cross-disciplinary disciplines, and 108 authorized master's degree programs in secondary disciplines; there are 15 authorized master's degree categories with a total of 96 professional fields; there are There are 5,356 faculty members (including 3,054 in affiliated hospitals), 1,451 full-time teachers, and more than 25,000 students, including 3,714 postgraduates and 19,000 undergraduates (including 3,838 in Kunlun College).}{QHU; 211 project; Double First-Class Strategic Plan}